Conceptual FD Figure

### 2021-07-26 analysis/conceptual_fig.Rmd
Create new column for y axis labels, save figure

low_rich <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("S") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(margin = margin(t = 0, r = 50, b = 0, l = 0)),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  ggtitle("Low")

low_rich

@@

Functional Richness
```{r}
low_fric <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-.5, 0,.25), 
  sd = rep(0.9, 3)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FRic") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(margin = margin(t = 0, r = 50, b = 0, l = 0)),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

low_fric

@@

Evenness 
```{r}
low_eve <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -2, -1.5, 0, 1.25, 3), 
  sd = c(1.25, 0.5, 1.25, 1.25, 0.65, 1.25),
  plot_range = c(2.5, 2, 2.5, 2.5, 2, 2.5)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, plot_range))) %>%
    select(-plot_range),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5.25, 5.25)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FEve") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(margin = margin(t = 0, r = 50, b = 0, l = 0)),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

low_eve

@@

Divergence 
```{r}
low_div <-  
ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -2, -1.5, 0, 1.25, 3), 
  sd = c(0.9, 0.9, 0.55, 0.5, 0.9, 0.9)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FDiv") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(margin = margin(t = 0, r = 50, b = 0, l = 0)),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

low_div

-.5, 0,.25
high_div <- 
ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -.5, -0.15, 0,.25, 3), 
  sd = c(0.55, 0.9, 0.9, 0.9, 0.9, 0.5)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

@@

plot_join <- plot_grid(low_rich, high_rich, low_fric, high_fric, 
                       low_eve, high_eve, low_div, high_div, 
                       nrow = 4, align = 'vh',
                       hjust = -1, axis = "l", scale = 0.9, 
                       label_x = "Trait Axis", label_y = "Abundance") #+
  #theme(plot.margin = margin(0, 0, 0, 30))

@@

# add_x <- ggdraw(add_sub(plot_join, "Trait Axis", 
#                y=2, x=0.5, hjust = 0.5, vjust=4.5))
# add_y <- add_sub(add_x, "Abundance",  
#                y=2, x=0.03, hjust = 0, vjust=0.5, angle = 90)
# ggdraw(add_y)
# 
# ggdraw(plot_join) + draw_label("Trait Axis", size = 14, hjust = 0.5, vjust = 0)

y.grob <- textGrob("Abundance", rot=90)

x.grob <- textGrob("Trait Axis")

grid.arrange(arrangeGrob(plot_join, left = y.grob, bottom = x.grob))

ggsave(here::here("figures/conceptual_fig.jpeg"))

 grid.arrange(arrangeGrob(p,p,p,p,top=textGrob("Sample Title One"), ncol=1), 
 arrangeGrob(p,p,p,p,top=textGrob("Sample Title Two"), ncol=1),   
 ncol = 2)
```
patchwork
```{r}
library(patchwork)
low_rich + high_rich + low_fric + high_fric + 
                       low_eve + high_eve + low_div + high_div + plot_layout(ncol = 2) %>%
  add_global_label(Ylab="Abundance", Ygap=0.05)
```

>>>>

low_rich <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("S") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank(),
        plot.title = element_text(hjust = 0.5)) +
  ggtitle("Low")

low_rich_fin <- low_rich + ylab(NULL)

@@

Functional Richness
```{r}
low_fric <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-.5, 0,.25), 
  sd = rep(0.9, 3)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FRic") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

low_fric_fin <- low_fric + ylab(NULL)

@@

Evenness 
```{r}
low_eve <- 
  ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -2, -1.5, 0, 1.25, 3), 
  sd = c(1.25, 0.5, 1.25, 1.25, 0.65, 1.25),
  plot_range = c(2.5, 2, 2.5, 2.5, 2, 2.5)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, plot_range))) %>%
    select(-plot_range),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5.25, 5.25)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FEve") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

low_eve_fin <- low_eve + ylab(NULL)

@@

Divergence 
```{r}
low_div <-  
ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -2, -1.5, 0, 1.25, 3), 
  sd = c(0.9, 0.9, 0.55, 0.5, 0.9, 0.9)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  ylab("FDiv") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_text(angle = 0, vjust = 0.5),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

low_div_fin <- low_div + ylab(NULL)

high_div <- 
ggplot(data.frame(x = c(-5, 5)), aes(x)) + 
  #stat_function(fun = dnorm, args = list(mean = -3, sd = .9), xlim = c(-5, -1)) +
  #stat_function(fun = dnorm, args = list(mean = 3, sd = .9), xlim = c(1, 5)) +
  pmap(tibble(mean = c(-3, -.5, -0.15, 0,.25, 3), 
  sd = c(0.55, 0.9, 0.9, 0.9, 0.9, 0.5)) %>%
    rowwise %>%
    mutate(xlim = list(get_xlim(mean, 2))),
  function(mean, sd, xlim) stat_function(fun = dnorm, args = list(mean = mean, sd = sd), xlim = unlist(xlim))
  )  +
  xlim(c(-5, 5)) +
  #ylim(c(0,1)) +
  scale_y_continuous(expand = expansion(mult = c(0, .1)), limits = c(.05, 1)) +
  theme_classic() +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

@@

plot_join <- plot_grid(get_plot_component(low_rich, "ylab-l"), low_rich_fin, high_rich, 
                       get_plot_component(low_fric, "ylab-l"), low_fric_fin, high_fric, 
                       get_plot_component(low_eve, "ylab-l"), low_eve_fin, high_eve, 
                       get_plot_component(low_div, "ylab-l"), low_div_fin, high_div, 
                       nrow = 4, align = 'vh',
                       hjust = -1, axis = "l", scale = 0.9, 
                       label_x = "Trait Axis", label_y = "Abundance")

@@

y.grob <- textGrob("Abundance",  
            gp = gpar(fontsize = 14),
            vjust = 15, rot=90)

x.grob <- textGrob("Trait Axis", hjust = -1.25)

final <- grid.arrange(arrangeGrob(plot_join, left = y.grob, bottom = x.grob))

ggsave(here::here("figures/conceptual_fig.jpeg"), final, height = 6, width = 7)

```
patchwork
```{r}
# library(patchwork)
# low_rich + high_rich + low_fric + high_fric + 
#                        low_eve + high_eve + low_div + high_div + plot_layout(ncol = 2) %>%
#   add_global_label(Ylab="Abundance", Ygap=0.05)
```
